Perturbing SU($n$)-symmetric interactions

### 2019-11-01 collective_sun/sun_perturbation.tex
minor wording changes

\newcommand{\e}{\varepsilon}

@@

We can recast the condition in \eqref{eq:cond_2} as an eigenvalue
problem by writing the coefficient matrix $\m w$ as a vector in
$\RR^{N^2}$,
\begin{align}
  \m w = \sum_{p,q} w_{pq} \op{p}{q}
  \to \v{\m w} \equiv \sum_{p,q} w_{pq} \ket{pq},
\end{align}
and defining the matrix
\begin{align}
  \check{\m h}
  \equiv \sum_{p,q} \bar h_{pq} \op{pq}
  + \sum_{p,q,\ell} h_{pq} \op{p\ell}{q\ell},
  \label{eq:h_super_mat}
\end{align}
in terms of which the condition in \eqref{eq:cond_2} becomes the
eigenvalue equation
\begin{align}
  \check{\m h} \c \v{\m w} = \f12 \Delta\p{\m w} \v{\m w}.
  \label{eq:cond_2_eig}
\end{align}
The matrix $\check{\m h}$ in \eqref{eq:h_super_mat} can be written in
the block-diagonal form
\begin{align}
  \check{\m h} = \sum_\ell \m h_\ell \otimes \op{\ell},
  &&
  \m h_\ell
  \equiv \sum_{p,q}\p{\delta_{pq} \bar h_{p\ell} + h_{pq}} \op{p}{q},
\end{align}
which reduces the eigenvalue equation in \eqref{eq:cond_2_eig} to the
$N$ smaller, independent eigenvalue equations
\begin{align}
  \m h_\ell \c \v{\m w}_\ell = \f12 \Delta\p{\m w} \v w_\ell,
  &&
  \v w_\ell \equiv \sum_p w_{p\ell} \ket{p}.
  \label{eq:cond_2_eig_block}
\end{align}
We can thus (numerically) diagonalize each of the blocks $\m h_\ell$,
and classify their eigenvectors $\v w_\ell$ by the corresponding
eigenvalues $\Delta\p{\m w}/2$.  ``Total'' eigenvectors $\v{\m w}$ of
$\check{\m h}$ are then built from eigenvectors $\v w_\ell$ within
each block $\m h_\ell$ that share the same eigenvalue
$\Delta\p{\m w}/2$.  The task of constructing eigenvectors
$\V_2\p{\m w}\ket\psi$ of $H_0$ and determining their energy thus
reduces to finding the eigenvectors and eigenvalues of $N$ matrices
$\m h_\ell$ of size $N\times N$.

>>>>

@@

We can recast the condition in \eqref{eq:cond_2} as an eigenvalue
problem by writing the coefficient matrix $\m w$ as a vector
$\v{\m w}$ in $\RR^N\times\RR^N$,
\begin{align}
  \m w = \sum_{p,q} w_{pq} \op{p}{q}
  \to \v{\m w} \equiv \sum_{p,q} w_{pq} \ket{pq},
\end{align}
and defining the matrix
\begin{align}
  \check{\m h}
  \equiv \sum_{p,q} \bar h_{pq} \op{pq}
  + \sum_{p,q,\ell} h_{pq} \op{p\ell}{q\ell},
  \label{eq:h_super_mat}
\end{align}
in terms of which the condition in \eqref{eq:cond_2} becomes the
eigenvalue equation
\begin{align}
  \check{\m h} \c \v{\m w} = \f12 \Delta\p{\m w} \v{\m w}.
  \label{eq:cond_2_eig}
\end{align}
The matrix $\check{\m h}$ in \eqref{eq:h_super_mat} can be written in
the block-diagonal form
\begin{align}
  \check{\m h} = \sum_\ell \m h_\ell \otimes \op{\ell},
  &&
  \m h_\ell
  \equiv \sum_{p,q}\p{\delta_{pq} \bar h_{p\ell} + h_{pq}} \op{p}{q},
\end{align}
which reduces the eigenvalue equation in \eqref{eq:cond_2_eig} to the
$N$ smaller, independent eigenvalue equations
\begin{align}
  \m h_\ell \c \v{\m w}_\ell = \f12 \Delta\p{\m w} \v w_\ell,
  &&
  \v w_\ell \equiv \sum_p w_{p\ell} \ket{p}.
  \label{eq:cond_2_eig_block}
\end{align}
We can (numerically) diagonalize each of the blocks $\m h_\ell$, and
classify their eigenvectors $\v w_\ell$ by the corresponding
eigenvalues $\Delta\p{\m w}/2$.  ``Total'' eigenvectors $\v{\m w}$ of
$\check{\m h}$ are then built from eigenvectors $\v w_\ell$ within
each block $\m h_\ell$ that share the same eigenvalue
$\Delta\p{\m w}/2$.  The task of constructing eigenvectors
$\V_2\p{\m w_\Delta}\ket\psi$ of $H_0$ and determining their energy
thus reduces to finding the eigenvectors and eigenvalues of $N$
matrices $\m h_\ell$ of size $N\times N$.
